RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-04-01 introduction.tex
yes

\item Coexistence. In the current data science ecosystem, the
isolation of exploratory visualization and data analysis
environments is a hinderance to wider adoption of modern techniques
on both sides. We specifically see the richness of interactive
visualization tools as still being isolated from the richness
of statistical programming environments.
(The path backward from production to analysis can be 
equally important: when problems discovered in
production require expert help, we would like experts to be
able to immediately apply the full range of analytic tools without
extracting data to move it back to the EDA environment.)
There is an opportunity to provide a framework so that developments
on either side are more easily employed by the other.
In addition, the integrated results should be more easily accessible
to the rest of the organization.

@@

RCloud uses the R language~\cite{RCoreTeam:2013:R} as the core set
of statistical analysis tools. As described in Section~\ref{sec:notebooks},
RCloud notebooks are sequences of R snippets interspersed with Markdown
for easy generation of reports. We also describe how RCloud enables
interactive visualization widgets in this setting (Section~\ref{sec:executinginbrowser}).

@@

The facilities for \emph{sharing, viewing and embedding} RCloud
notebooks address technology transfer.
Because RCloud embraces technologies that are part of the computing
environment (specifically, inter-process communication via HTTP and
web services as remote procedure calls), it is not complicated to
integrate RCloud with satellite efforts in corporate environments.

@@

In Section~\ref{sec:limitations}, we discuss some consequences of
designing for a single language, and how this was received by
our (small, but active) user community.

>>>>

\item Coexistence. In the current data science ecosystem, the
isolation of exploratory visualization and data analysis
environments is a hinderance to wider adoption of modern techniques
on both sides. We specifically see the richness of interactive
visualization tools as still being isolated from the richness
of statistical programming environments.
%(The path backward from production to analysis can be 
%equally important: when problems discovered in
%production require expert help, we would like experts to be
%able to immediately apply the full range of analytic tools without
%extracting data to move it back to the EDA environment.)
There is an opportunity to provide a framework so that developments
on either side are more easily employed by the other.
In addition, the integrated results should be more easily accessible
to the rest of the organization.

@@

@@

RCloud uses the R language~\cite{RCoreTeam:2013:R} as the core set
of statistical analysis tools.  The facilities for \emph{sharing, viewing
and embedding} RCloud notebooks address the {\bf technology transfer} requrement.
Because RCloud embraces technologies that are part of the computing
environment (specifically, inter-process communication via HTTP and
web services as remote procedure calls, as explained
in Section~\ref{sec:highlevelarchitecture}), it is straightforward to
integrate RCloud with satellite efforts in corporate environments.

{\bf Coexistence} between analysis and visualization is supported in
its human interface architecture, described in~\ref{sec:humaninterface}. 
As oulined in Section~\ref{sec:notebooks}, RCloud notebooks are sequences
of R snippets interspersed with Markdown for easy generation of reports.
We describe how RCloud enables interactive visualization widgets in
this setting (Sections~\ref{sec:Rinbrowser} and~\ref{sec:interactivenotebooks}).
Indexing, publishing and sharing of notebooks is also the main way
Rcloud supports {\bf discoverability}.

@@

Section~\ref{sec:casestudy} describes a case study illustrating some of these concepts.

In Section~\ref{sec:limitations}, we report on experience toward meeting
these requirements in RCloud, and limitations encountered.
